\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[colorlinks=true,linkcolor=blue,anchorcolor=blue,citecolor=blue,filecolor=blue,menucolor=blue,runcolor=blue,urlcolor=blue]{hyperref}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape \textbf{Muhammad Naufal Pratama}}\\
	\href{mailto:muhammadnaufalp@students.undip.ac.id}{muhammadnaufalp@students.undip.ac.id} $\cdot$ \href{https://wa.me/6282133617483}{+62 82133617483} $\cdot$ \href{https://linkedin.com/in/mnpratamaa}{LinkedIn} $\cdot$ \href{https://github.com/mhnaufal}{Github} $\cdot$ \href{mprtmma.medium.com}{Medium}\\
\end{center}

Highly passionate about the technology world with a bunch of experiences in website and software development especially on backend side with the ability to teach as well as system programming and game development for hobbies\\

%==== Experience ====%
\header{Experiences}
\vspace{1mm}

\textbf{Internship} \hfill Fita\\
\textit{DevOps/SRE Intern} \hfill June 2022 - Present\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Having internship as the DevOps/SRE intern at \href{https://fita.co.id/}{Fita} that works closely with CI/CD Pipeline, Google Cloud Platform, Kubernetes, and Terraform.
\end{itemize}

\textbf{Generasi GIGIH 2.0} \hfill Kampus Merdeka \\
\textit{Backend Engineering Track} \hfill Feb 2022 - Present\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Participate and gain a lot of insight in \href{https://www.anakbangsabisa.org/generasi-gigih/}{Generasi GIGIH 2.0} program held by Yayasan Anak Bangsa Bisa, (YABB). Taking the Backend Engineer track and learning about Ruby, MVC, OOP, TDD, and much more through online courses and a capstone project.
\end{itemize}

\textbf{Internship} \hfill UPT Perpustakaan UNDIP \\
\textit{Fullstack Engineer Intern} \hfill Feb 2022 - Present\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Work eagerly as a full-stack engineer to develop an automated mail template platform for helping library staff write an office letter without manually writing it through a word editor. Tech stack used: Laravel, Bootstrap, Redis, RabbitMQ, Heroku. \href{http://template-surat-testing.herokuapp.com/}{Preview page here!}
\end{itemize}

\textbf{IEEE SB-Undip Organization} \hfill Universitas Diponegoro\\
\textit{Web Division Committe} \hfill July 2021 - May 2022\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Construct and manage \href{https://edu.ieee.org/id-undip/}{IEEE SB-Undip} the website using WordPress and coordinate website development training named IWT (IEEE Website Training).
\end{itemize}

\textbf{Mulo} \hfill Wonosobo \\
\textit{Backend Engineer} \hfill Feb 2021 - Present\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Develop backend API intensively and also the \href{https://play.google.com/store/apps/details?id=app.mulo}{android app} for \href{https://muloapp.id/}{Mulo}, which is a startup company focusing on empowering UMKM in Indonesia by providing an application that can help manage UMKM activities and finances using blockchain technology, using NodeJS, SailsJS, Kotlin, Git, and Heroku as the tech stacks.
\end{itemize}

\textbf{Azura Labs} \hfill Semarang, Jawa Tengah\\
\textit{Backend Engineer Intern} \hfill Jan 2021 - Mar 2021\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Develop backend REST API using Laravel for a web-based project called \textquotesingle{}Butiko\textquotesingle{}, which contains articles and activities carried out by the \textquotesingle{}\href{https://butiko.id/}{Butiko}\textquotesingle{} community.
\end{itemize}

\textbf{Lab Assistant} \hfill Universitas Dipoengoro\\
\textit{Fundamental of Programming Lab Assistant} \hfill Aug 2020 - Des 2020\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Educate and enlighten students about the fundamental of programming with functional as the paradigm and Python as the programming language.
\end{itemize}

%==== Education ====%
\header{Education}
\textbf{Universitas Diponegoro}\hfill Semarang, Jawa Tengah\\
Majoring in \textbf{Informatics} \textit{GPA: 3.84} \hfill 2019 - 2023 (Expected)\\
Taking specialize in software engineering and system programming.
\vspace{2mm}

%==== Projects ====%
\header{Projects}
{\textbf{COBLOS}} {\sl Laravel, Bootstrap, Git} \hfill \href{https://coblos.herokuapp.com/}{COBLOS}\\
Contribute as the backend programmer in developing a survey web-based application that helps companies or individuals manage their surveys.\\
\vspace*{2mm}

{\textbf{Siperpus}} {\sl Laravel, SailsJS, Bootstrap, Git} \hfill \href{http://sisperpus.herokuapp.com/}{sisperpus} | \href{https://pbp-siperpus.herokuapp.com/}{API}\\
Give an extraordinary contribution as the backend programmer for this project and great teamwork. Siperpus is a library management system developed using Laravel. \\
\vspace*{2mm}

{\textbf{Anforom 2021}} {\sl Laravel, JavaScript, Github} \hfill \href{https://anforcom.com}{Anforcom}\\
Took charge as a backend programmer in creating, developing, and maintaining Anforcom's website, which is a competition and seminar that is held annually by the HMIF Undip.\\
\vspace*{2mm}

{\textbf{Mulo}} {\sl NodeJS, SailsJS, Kotlin, Git} \hfill \href{https://muloapp.id/}{Mulo}\\
Develop backend API intensively for Mulo, which is a startup company focusing on empowering UMKM in Indonesia by providing an application that can help manage UMKM activities and finances using blockchain technology\\
\vspace*{2mm}

{\textbf{Software Defect Prediction}} {\sl Python} \hfill \href{https://github.com/mhnaufal/Software-Defect-Finale/blob/main/reports/PAPER-Software%20Defect%20Prediction.pdf}{Paper}\\
Research and explore in-depth defects in software using machine learning and deep learning algorithms such as CNN, LSTM, and Random Forest from the experiments until journal publications.\\
\vspace*{2mm}

{\textbf{RS NUMedika}} {\sl HTML, CSS, JavaScript} \hfill \href{http://rsnuwonosobo.com/}{RS NUMedika}\\
Improve the frontend landing page website for RS NUMedika Wonosobo.\\
\vspace*{2mm}

\

%==== Certifications ====%
\header{Certifications \& Courses}
\textbf{Text Retrieval and Search Engines} \hfill University of Illinois offered through Coursera\\
Digest knowledge about information and text retrieval and grasp how a search engine works. \hfill \textit{Aug 2021}\\
\vspace*{2mm}

\textbf{Belajar Membuat Aplikasi Back-End untuk Pemula} \hfill Dicoding Indonesia\\
Graduate marvelously on how to implement RESTfull API using HapiJS, a NodeJS framework for creating API. \hfill \textit{Jun 2021}\\
\vspace*{2mm}

\textbf{Belajar Dasar Pemrograman Javascript} \hfill Dicoding Indonesia\\
Succeeded learn and implementing JavaScript fundamental for web development. \hfill \textit{May 2021}\\
\vspace*{2mm}

\textbf{Belajar Dasar Pemrograman Python} \hfill Dicoding Indonesia\\
Study on fundamental Python programming language. \hfill \textit{Mar 2021}\\
\vspace*{2mm}

\textbf{Cyber Security Essential} \hfill Cisco Networking Academy\\
Having a good understanding on the tactics, techniques, and procedures \\used by cyber criminals in cyber security world. \hfill \textit{Feb 2020}\\
\vspace*{2mm}

%==== Skills ====%
\header{Skills}
\begin{tabular}{ l l }
	Hard Skills:              & C, Rust, Python, PHP, JavaScript, Go, SQL, Laravel, NodeJS, Git, PostgreSql, AWS\\ & Insomnia, MySql, Heroku, Redis, RabbitMQ, Docker\\
	Soft Skills:                    & Analytical skill and time management\\
\end{tabular}
\vspace{2mm}

\ 
\end{document}